---
title: "Maximizing TURF profit through different closure strategies"
author: "Caio Faro & Juan Carlos Villase?or"
date: "November 16, 2016"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## __Project Set Up__

- A 100 km^2^ TURF (Territorial Use Rights for Fishing), in a 10 by 10 km polygon. 

- The fishers have heard about an option to enhance the productivity and the income by closing fishing grounds within the TURF (i.e. a TURF-reserve).

- By having a no-take area, the TURF will benefit from the spillover (i.e. organisms that step out of the reserve).

- The community seeked consultation to find the optimum way in which they can maximize profits.


## __Strategies__

1) __Permanent closure__: Close a percentage of the TURF for the whole time of the concession and get benefits from spillover.

2) __Temporal closure__: Close a percentage of the TURF for $T*$ years, allowing the population to recover, then open the reserve and allow fish for a year before closing again.


## __Assumptions__

- The TURF is divided into parcels of 1 by 1 km.
- Each parcel of the concessioned area has a starting density of $$N_0 = \frac{K}{2}$$
- Movement wrapped at the edges of the TURF (Ovando *et al.*, 2016).
- Organisms are recruited once a year, with no age or size structure.
- Fishing effort (__*u*__) outside the reserve is equal for every parcel.
- Price and costs are constant through time.


## __Data__

- Data from Quintana Roo provided by Comunidad y Biodiversidad A.C. (COBI).
- Data colected through transects inside the reserves.
- Parameters __*r*__ and __*K*__ were estimated optimizing model fit with solver.
$$N_{t+1}=N_t+rN_t\left(1-\frac{N_t}{K}\right)$$
- Parameters __*m*__ and __*u*__ were randomly selected.


## __Parameters__

- Growth rate ($r$) = 1.0834
- Carrying capacity ($K$) = 0.0532 organisms/m^2^
- Movement rate ($m$) = 0.5
- Catch rate ($u$) = 0.6
- Price ($p$) = US$ 20/lobster
- Cost ($c$) = US$ 730/year
- Discount rate ($d$) = 0.05


## __Equations__

$N_{i,j,t+1} = N_{i,j,t} + N_{i,j,t}r\left(1-\left(\frac{N_{i,j,t}}{K}\right)\right) - U_{i,j,t} + M_{i,j,t} - E_{i,j,t}$

$U_{i,j,t} = u_{i,j,t}N_{i,j,t}$

$E_{i,j,t} = m\left((1-u_{i,j,t})N_{i,j,t}\right)$

$M_{i,j,t} = \left(\frac{m}{4}(1-u_{i,j,t})\right)(N_{i-1,j,t} + N_{i+1,j,t} + N_{i,j-1,t} + N_{i,j+1,t})$

$C_t = \sum_{i=1}^{n} \sum_{j=1}^{n} u_{i,j,t}N_{i,j,t} \sum_{i=1}^{n} \sum_{j=1}^{n} U_{i,j,t}$

$R_t = C_tp-c$


## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

