---
title: "Maximizing TURF profit through different closure strategies"
author: "Caio Faro & Juan Carlos Villase?or"
date: "November 16, 2016"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## __Project Set Up__

A fishing community in the Caribbean has been awarded with the concession of an area to fish lobster for 50 years, starting in 2017. This area, known as a TURF (Territorial Use Rights for Fishing) has 100 km^2^ , in a 10 by 10 km polygon. The community has exclusive access to this TURF, and are not allowed to fish elsewhere. 

The fishers have heard from nearby communities about an option to enhance the productivity and the income by closing fishing grounds within the TURF (i.e. a TURF-reserve), and have seeked consultation to find the optimum way in which they can maximize profits.

The reasoning for the implementation of a TURF-reserve is that by having a no-take area, the TURF will benefit from the spillover (i.e. organisms that step out of the reserve).


## __Strategies__

1) __Permanent closure__: Close a percentage of the TURF to get benefits from spillover. The reserve will remain closed forever, and we would have to find the optimum size of the reserve that maximizes profits.

2) __Temporal closure__: Close a percentage of the TURF for some years, allowing the population to recover. Then, after t years open the reserve and allow fish within the reserve with the same effort as outside. After that, the reserve is closed for $T*$ years again.


## __Assumptions__

- The TURF is divided into parcels of 1 by 1 km.
- Each parcel of the concessioned area has a starting density of $$N_0 = \frac{K}{2}$$.
- Movement wrapped at the edges of the TURF (Ovando *et al.*, 2016).
- Organisms are recruited once a year, with no age or size structure.
- Fishing effort (__*u*__) outside the reserve is equal for every parcel.
- Price and costs are constant through time.


## __Data__

- Data from Quintana Roo provided by Comunidad y Biodiversidad A.C. (COBI).
- Data colected through transects inside the reserves.
- Parameters __*r*__ and __*K*__ were estimated __based on__.
- Parameters __*m*__ and __*u*__ were randomly selected.


## __Parameters__

- Growth rate ($r$) = 
- Carrying capacity ($K$) = 
- Movement rate ($m$) = 
- Catch rate ($u$) = 
- Price ($p$) = US$ 20/lobster
- Cost ($c$) = US$ 730/year
- Discount rate ($d$) = 0.05


## __Equations__

$$N_{i,j,t+1} = N_{i,j,t} + N_{i,j,t}r\left(1-\left(\frac{N_{i,j,t}}{K}\right)\right) - U_{i,j,t} + M_{i,j,t} - E_{i,j,t}$$

$$U_{i,j,t} = u_{i,j,t}N_{i,j,t}$$

$$E_{i,j,t} = m\left((1-u_{i,j,t})N_{i,j,t}\right)$$

$$M_{i,j,t} = \left(\frac{m}{4}(1-u_{i,j,t})\right)(N_{i-1,j,t} + N_{i+1,j,t} + N_{i,j-1,t} + N_{i,j+1,t})$$

$$C_t = \sum_{i=1}^{n} \sum_{j=1}^{n} u_{i,j,t}N_{i,j,t} \sum_{i=1}^{n} \sum_{j=1}^{n} U_{i,j,t}$$

$$R_t = C_tp-c$$


## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

